\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-12-15 Manuscript/Manuscript.tex
added to discussion section

Alongside this method, the cumulative curve method as used to extract traffic flow data from videos \cite{6Pu2017}. Equation \ref{eq:3} gives the basic model of the generalized linear model:
\begin{equation}\label{eq:3}
Y_{nx1} = X_{nxp}\beta_{px1}+\epsilon_{nx1}
\end{equation}
Where the matrix of observed values of dependent variables is  $Y_{nx1}$, $X_{nxp}$ is the matrix of observed explanatory variables, $\beta_{px1} =$ is the matrix of coefficients for explanatory variables, and $\epsilon_{nx1}$ is the error. Using this model is reported to help to understand how each factor contributed to the delay of cyclists on urban streets. In Figure ~\ref{fig:traffic}, the results are shown of results of the significance of multiple variables on vehicle delay, and it can be seen that with this method, bicycle and vehicle flow as well as the number of vehicle lanes, has a significant effect on vehicle delay. The results of flow vs. density are also shown in Figure ~\ref{fig:flow}, and reveals that the average bicycle speed decreases slightly as the density increases while  the flow is still increasing, and  when there is high density the variation of bicycle speed decreases a great deal. These results are also consistant across multople locations of urban streets. 
\begin{figure}[hbt!]
    \centering \includegraphics[width=1\textwidth]{BikeTrafficResults.png}
    \caption{Results table from Research on Bicycle Traffic from Pu et al.}
    \label{fig:traffic}
\end{figure}

@@

The different types of cycling infrastructure, especially bike lanes, are shown in this body of research to have a significant impact on increasing cycling ridership. Whether it's an increase in bike-shares or commutership, this relationship is shown in the papers. This is essential when it comes to appealing to policy makers and decision makers in communities to convince them to add cycling infrastructure to their area. Statistical analyses are influential in providing actionable insights, including the correlation between infrastructure types existing in an area and increased cycling. \par

Studies like \citet{1MateoBabiano2016} show how effective simple methods like Spearman's correlation coefficient can be at revealing the impact of bike lanes on PBSP usage. These sorts of results can lead to insights for urban planners when it comes to designing cities. \par

Predictive models were also used, like binary regression models in \citet{2Yujun2019} to provide insight into all the factors influencing an individuals' choice to cycle for commuting. These predictive models offer ways for policy makers to encourage cycling as a successful commuting option in their cities.\par

Some future directions this field could go include focusing on more that just high socioeconomic areas. This type of research has only really been done in affluent countries, likely because a lot of the research has been based off of bike-share systems. Which leads into another point of improvements, where there could be better ways of collecting data on cyclists, as they are often excluding people who own their own bikes from the data. Additionally, there is room for more cost-benefit analyses on the economic impact of investing in cycling infrastructure. When you create such infrastructure, there could be less congestion and damage to the automobile infrastructure. Which would be beneficial to persuading policy makers towards creating more bike lanes and encouraging cycling.

>>>>

Alongside this method, the cumulative curve method as used to extract traffic flow data from videos \cite{6Pu2017}. Equation \ref{eq:3} gives the basic model of the generalized linear model:
\begin{equation}\label{eq:3}
Y_{nx1} = X_{nxp}\beta_{px1}+\epsilon_{nx1}
\end{equation}
Where the matrix of observed values of dependent variables is  $Y_{nx1}$, $X_{nxp}$ is the matrix of observed explanatory variables, $\beta_{px1} =$ is the matrix of coefficients for explanatory variables, and $\epsilon_{nx1}$ is the error. Using this model is reported to help to understand how each factor contributed to the delay of cyclists on urban streets. In Figure ~\ref{fig:traffic}, the results are shown of results of the significance of multiple variables on vehicle delay, and it can be seen that with this method, bicycle and vehicle flow as well as the number of vehicle lanes, has a significant effect on vehicle delay. The results of flow vs. density are also shown in Figure ~\ref{fig:flow}, and reveals that the average bicycle speed decreases slightly as the density increases while  the flow is still increasing, and  when there is high density the variation of bicycle speed decreases a great deal. These results are also consistent across multiple locations of urban streets. 
\begin{figure}[hbt!]
    \centering \includegraphics[width=1\textwidth]{BikeTrafficResults.png}
    \caption{Results table from Research on Bicycle Traffic from Pu et al.}
    \label{fig:traffic}
\end{figure}

@@

Investing in different types of cycling infrastructure, especially separated bike lanes, is shown in this body of research to have a significant impact on increasing cycling ridership. Whether it's an increase in bike-shares or commutership, this relationship is shown in the papers. This is essential when it comes to appealing to policy makers and decision makers in communities to convince them to add cycling infrastructure to their area. Statistical analyses are influential in providing actionable insights, including the correlation between infrastructure types existing in an area and increased cycling. \par

Studies like \citet{1MateoBabiano2016} show how effective simple methods like Spearman's correlation coefficient can be at revealing the impact of bike lanes on PBSP usage. These sorts of results can lead to insights for urban planners when it comes to designing cities. Predictive models were also used, like binary regression models in \citet{2Yujun2019} to provide insight into all the factors influencing an individuals' choice to cycle for commuting. These predictive models offer ways for policy makers to encourage cycling as a successful commuting option in their cities.\par

Some future directions this field could go include focusing on more than just high socioeconomic areas. This type of research has only really been done in affluent countries, likely because a lot of the research has been based off of bike-share systems. Which leads into another point of improvements, where there could be better ways of collecting data on cyclists, as they are often excluding people who own their own bikes from the data. Additionally, there is room for more cost-benefit analyses on the economic impact of investing in cycling infrastructure. When you create such infrastructure, there could be less congestion and damage to the automobile infrastructure. Which would be beneficial to persuading policy makers towards creating more bike lanes and encouraging cycling. Further improvements in the field of statistical modeling to conduct bike lane research include using longitudinal studies, to track changes and trends, rather that just cross-sectional research at one point in time. \par

In addition, there is a lack of spatial analysis models in the current body of research on cycling infrastructure. These models, particularly spatial regression, Geographically Weighted Regression (GWR), or spatial auto correlation analysis, would be valuable for understanding spatial patterns. For instance, clustering of bike lane usage, or identifying hot-spots of accidents and injuries along bike lanes \cite{Kanade_2022}. It could also be beneficial to include causal inference techniques when studying cycling infrastructure. These tools, like directed acyclic graphs and instrumental variable analysis, could be appropriate for investigating the causal impact of interventions or policy changes related to bike lane infrastructure on outcomes like safety or usage of the infrastructure \cite{Pearce_Lawlor_2016}.
